Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-02-05 Paper/paper.tex
Clarifying further

Figure~\ref{fig:ConceptFigure} shows the different parts of our method for a 1D periodic signal for illustration purposes. In general, the actual input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$. We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$. The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}, which we split into two parts: an analysis part (a) and a synthesis part (b).  For the analysis part, we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}. Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved. Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved. Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for the steps in (a) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.  We also use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $\mb{P}$ to mitigate drift.

>>>>

Figure~\ref{fig:ConceptFigure} shows the different parts of our method for a 1D periodic signal for illustration purposes. In general, the actual input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$. We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$. The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}, which we split into two parts: an analysis part (a), which culminates in phase estimates $\phi$, and a synthesis part (b), in which the template is created based on information in (a).  For the analysis part, we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}. Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved. Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved. Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for the steps in (a) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.  We also use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $\mb{P}$ to mitigate drift.
